Supplimentary Analysis

### 2021-11-07 Appendix-B.tex
* supplementary analysis on EFA (Minimum residulas and six-factor solution) is added
Some minor formating here and there.

\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB)
\end{figure}

@@

\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
\end{figure}
\end{appendix}

>>>>

\caption{\label{tab:tabDesAppB-50}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-52-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB-52)
\end{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-56-1}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-56)
\end{figure}

@@

\caption{\label{tab:EFATableAppB-59}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-60-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-60)
\end{figure}
\end{appendix}
